Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-14 latex/ms.tex
add timeline chart as figure 1a in main text

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled in the first and second year, respectively, which are identified as young-of-year individuals without errors. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year. It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later. Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations. For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively.

In the example depicted in {\bf Fig~\ref{cartoon}}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed. In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs. The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{{\bf FIGURE 1} \figcapa{}}
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%

>>>>

To estimate the migration number or rate, we utilize the number of HS and/or PO pairs observed in a sample. In the both populations, $n_{\rm O, 1}$ and $n_{\rm O, 2}$ offspring are randomly sampled in the first and second year, respectively, which are identified as young-of-year individuals without errors. Additionally, $n_{\rm P, 1}$ and $n_{\rm P, 2}$ parents are randomly sampled immediately after the end of the reproductive season in the first and second year, respectively. For mathematical tractability, parents have to survive during the reproductive season; therefore, both mother and father of a certain offspring have a potential to be sampled even in the same year. It should be noted that all the four kinds of a sample (i.e., $n_{\rm P, 1}$, $n_{\rm P, 2}$, $n_{\rm O, 1}$, and $n_{\rm O, 2}$) are not always required for estimating migration number or rate; what kinds of a sample are needed depends on the situation, as explained later. Up to the subsection 2.6, we only focus HS pairs and PO pairs found between the two populations. For the applicability of fishery management, we assume invasive sampling procedure, preventing the finding of a parent-offspring pair such that a parent and offspring is sampled in the population 1 and 2, respectively. {\bf Figure~\ref{cartoon}a} illustrates a timeline of sampling scheme for hypothetical populations.

In the example depicted in {\bf Fig~\ref{cartoon}b}, five offspring and four parents are sampled in the population 1 and four offspring and six parents are sampled in the population 2, and two HS and one PO pairs found between the two populations are observed. In addition, there are several PO pairs observed within the same population, which are available to estimate parent numbers, as explain the next section. In our modeling framework, if full-sibling (FS) relationship is found, we count it as two HS pairs. The numbers of HS and PO pairs found between the two populations are determined by pairwise comparison of all the sample individuals ($n_{\rm O,1}\times n_{\rm O,2}$ and $n_{\rm O,1}\times n_{\rm P,2}$ comparisons, respectively).

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{{\bf FIGURE 1} \figcapa{}}
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%
